Towards Systematic Specification and Verification of Fault-Tolerant Protocols

### 2016-06-14 doc/om-paper/paper.tex
more paper text

\lee{finish intro...}

@@

\subsection{Synchronous Observers}\label{sec:sync}
Synchronous observers are state machines that are synchronously composed with a system specification to check properties over the system's state variables. Synchronous observers are a method for composing specifications with a program. Synchronous observers were first introduced in the context of the synchronous programming languages, such as Lustre~\cite{}. While synchronous observers have been part of model-checking folklore for some time, Rushby systematically describes their application to the domain~\cite{}. The general form for specifying synchronous observers is the following:
$$system | assumptions | requirements$$
\noindent
where `$|$' denotes synchronous composition of state machines.

\paragraph{Fault model}

\paragraph{Property Observer}

@@

>>>>

\lee{finish intro...  One more contribution is that we abstract faults using partially interpreted functions in model-checking, which is new? Note focus is on infinite-state model-checking}

@@

\subsection{Synchronous Observers}\label{sec:sync}
Synchronous observers are state machines that are synchronously composed with a system specification to check properties over the system's state variables. Synchronous observers are a method for composing specifications with a program. Synchronous observers were first introduced in the context of the synchronous programming languages, such as Lustre~\cite{}. While synchronous observers have been part of model-checking folklore for some time, Rushby systematically describes their application to the domain~\cite{}. The general form for specifying synchronous observers is the following:
$$system | assumptions | requirements$$
\noindent
where `$|$' denotes synchronous composition of state machines. The assumptions constrain the system's state variables, while the requirements monitor the system's state variables.

The benefit of the synchronous observer approach is that we can develop a system specification that contains no extraneous modeling context from which to synthesize an implementation. For example, we do not want synthesize an implementation that injects faults! Furthermore, modifying assumptions and requirements is simpler when they are not distributed throughout the model.

%% As a simple example, consider the following transition system. In the following, \texttt{'} denotes the next-state value of a variable, and texttt{-->} is a two-place operator, preceded by a guard, such that if the guard is true, the state update following the arrow is applied. One transition with a true guard is nondeterministically applied.

%% \begin{verbatim}
%% system:
%%   initialization: i = 0, b = True
%%   transitions:
%%     b == True  --> i' = i+2, b' = False
%%     b == False --> i' = i-1, b' = True
%% \end{verbatim}

%% The linear temporal logic (LTL) property \texttt{G(i >= 0)} holds for this system. Let us define a requirements transition system to check the same property:

%% \begin{verbatim}
%% requirements:
%%   initialization: nonneg = True
%%   transitions:
%%     i >= 0 -->
%% \end{verbatim}

\subsection{Property Observer}

% ------------------------------------------------------------
\section{The Synchronous Kibitzer}
The typical approach to injecting faults into a formal model of a distributed system is to add a new state variables to each process representing its fault state. Then additional state variables are added to represent the nondeterminism introduced by faults into the state or messages by a process. Finally, additional transitions are added to each process to modify the process's state or messages based on it's current fault state.

This straightforward approach introduces substantial additional state and nondeterminism, reducing the scalability of model-checking. Modeling faults is particularly expensive given that additional state and nondeterminism is added to each process. These scalability issues are noted throughout the literature. For example, \lee{TTA startup paper, helmut's paper, etc.}

Not only is modeling faults expensive, but it is generally non-compositional. For example, to model-check the Oral Messages algorithm~\cite{} that provides interactive consistency in the presence of Byzantine faults, Rushby every transition of the General and Lieutenant processes acts on their fault state~\cite{}.

Another difficulty with adding faults to a model is that the number of states that must be introduced may be dependent non-obviously on other aspects of the fault model, specific protocol, and system size. Furthermore, since SAT-based model-checking is NP-complete, it is important not to introduce any state beyond the minimal required. Such constraints lead to ``meta-model'' reasoning, such as the following, as described by Rushby:

\begin{quote}
To achieve the full range of faulty behaviors, it seems that a faulty source should be able to send a different incorrect value to each relay, and this requires n different values. It might seem that we need some additional incorrect values 3 so that faulty relays can exhibit their full range of behaviors. It would certainly be safe to introduce additional values for this purpose, but the performance of model checking is very sensitive to the size of the state space, so there is a countervailing argument against introducing additional values. A little thought will show that the way faulty relays have their most significant impact is by tipping the majority vote in a receiver one way or the other, and this can only be achieved if they use the same values as nonfaulty relays. Hence, we decide against further extension to the range of values~\cite{}.
\end{quote}

To address these problems, we introduce a synchronous observer that injects faults that we call a \emph{synchronous kibitzer}. The kibitzer decomposes the state and transitions associated with the fault model from the system.

For the sake of concreteness, we introduce
 under the hybrid fault model of Thambidurai and Park~\cite{}. The fault model distinguishes Byzantine (or arbitrary), symmetric, and manifest faults. This fault model applies to broadcast systems, in which a process is expected to broad the same value to multiple receivers. A Byzantine faulty

@@

\lee{let's also check out scalability when we ``turn off'' faults. Also, how hard is it to turn them off or change the fault model? E.g., how many lines of spec need to be changed? Compare to rushby's?}
